---
title: "DV_TProject1"
output: html_document
---

**Authors: Rolando Melendez, Hyunji Seo, Catherine Tu**

##This is how our RStudio is configured:
```{r}
sessionInfo()
```
***
##Program file structure
  00 Doc - contains .Rmd and .html 
  
  01 Data - contains the code to Extract, Transform, and Load our data 
  
  02 Tableau - this is where the Tableau workbook goes, make it a twb file 
  
  03 R SQL Visualizations - contains our workflows and the code for the visualizations

***  
##Data summary and subset
```{r}
#Shows the subset and summary of the data frame
#source("../01 Data/R_ExtractTransform.R", echo = TRUE)
source("../01 Data/R_Load.R", echo = TRUE)
```

####Explanation of Data:
This data relates to the direct marketing campaign of a Portuguese bank to have people subscribe to a term deposit at their institution. The campaign had gathered data regard their campaign efforts, individuals' demographics, and external social situations at the time of the campaign. 

##Scatter Plot
```{r}
#Shows the subset and summary of the data frame
source("../03 R SQL Visualizations/ScatterPlot.R", echo = TRUE)
```

####Method:

####Findings:

***

##Cross Tab and KPI
```{r}
#Shows the subset and summary of the data frame
source("../03 R SQL Visualizations/Crosstab_KPI.R", echo = TRUE)
```

####Method:

####Findings:

***

##Bar Chart and Reference Line
```{r}
#Shows the subset and summary of the data frame
source("../03 R SQL Visualizations/Barchart_RLine.R", echo = TRUE)
```

####Method: 

####Findings:

***
